Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
add one giant table for feedback

# Team descriptives
tbl_team_desc <- msa_models %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  add_row(.before = 1, 
    metric = "size", 
    min = team_desc_df %>% filter(stage == "Final") %>% pull(min), 
    max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
    avg = team_desc_df %>% filter(stage == "Final") %>% pull(mean_size), 
    sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
  mutate(across(-metric, specify_decimal, k = 1)) %>% 
  mutate(desc = "team_desc", 
   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min}--{max}"), 
    Metric = case_when(
      metric == "size" ~ "Team size", 
      metric == "years_from_phd" ~ "Years since PhD", 
      metric == "stat_rating" ~ "Self-report statistical ability", 
      metric == "prior_belief" ~ "Prior belief in $H_{1}$", 
      metric == "phon_rating" ~ "Acoustic analysis rating", 
      metric == "all_rating" ~ "Overall peer review rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)

@@

# Model descriptives 
tbl_model_desc <- msa_models %>% 
  select(animal, n_predictors:n_random, n_models) %>% 
  group_by(animal) %>% 
  summarize(across(everything(), mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
  mutate(desc = "model_desc", 
    metric = fct_relevel(metric, "n_models"), 
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min}--{max}"), 
    Metric = case_when(
      metric == "n_coefficients" ~ "n. coefficients", 
      metric == "n_models" ~ "n. models", 
      metric == "n_predictors" ~ "n. predictors", 
      metric == "n_random" ~ "n. random effects", 
      metric == "n_random_int" ~ "n. random intercepts", 
      metric == "n_random_slo" ~ "n. random slopes", 
      metric == "n_random_smooth" ~ "n. random smooths",
      metric == "n_terms" ~ "n. terms"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

@@

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", sd)`) models per team. 
Table \@ref(tab:team-descriptives-table) provides a summary of the contributing teams and their analyses. 
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

<!-- Begin Table 1 --> 
\vspace{0.2in}
```{r}
#| label: team-descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc, 
  filter(tbl_model_desc, label == "model_desc_n_models")
  ) %>% 
  select(Metric, Range, `Mean (SD)`) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "c", "r"), 
    caption = "Descriptive statistics for teams included in the 
    meta-analysis (n = 30).",
    label = "team-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)
```
<!-- END: Table -->

@@

`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models used acoustic measures taken at the level of the segment (e.g. comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g. comparing the acoustic profile of *Banane* 'banana'), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g. the noun phrase including determiner and adjective, e.g. "the green banana"), `r round(window_n[[4,1]],2) * 100`\% from the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence. 
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
Table \@ref(tab:categorical-descriptives-table) provides a summary of the acoustic analyses.

<!-- Begin Table 2 --> 
\vspace{0.2in}
```{r}
#| label: categorical-descriptives-table
#| results: 'asis'

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
An appropriate way to account for this non-independence is by using models that include so-called random or group level effects [e.g., @gelman2006data; @schielzeth2009conclusions], variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication]. <!-- TR: Did we confirm this? -->
`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
Table \@ref(tab:stats-descriptives-table) provides a summary of the statistical analyses.

<!-- Found effect 
JVC: this code is ready to go, but not all the rows in the google sheet are 
filled out (approx. 40 missing)
--> 
```{r}
#| label: found-effect
#| echo: false

@@

<!-- Begin Table 3 --> 
```{r}
#| label: stats-descriptives-table
#| results: 'asis'
tbl_model_desc %>% 
  select(Metric, Range, `Mean (SD)`) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. "), 
         Metric = str_to_sentence(Metric)) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "c", "r"), 
    caption = "Descriptive statistics for statistical analyses included in the 
    meta-analysis (n = 30).",
    label = "stats-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)
```
<!-- END: Table -->

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:team-descriptives-table)).
The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).
For reference, as mentioned in the Methods section, a score of 75 was defined as "an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation", indicating that on average reviewers judged the provided analyses to be appropriate, although "imperfect".

>>>>

# Team descriptives
tbl_team_desc <- msa_models %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  add_row(.before = 1, 
    metric = "size", 
    min = team_desc_df %>% filter(stage == "Final") %>% pull(min), 
    max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
    avg = team_desc_df %>% filter(stage == "Final") %>% pull(mean_size), 
    sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
  mutate(across(-metric, specify_decimal, k = 1)) %>% 
  mutate(desc = "team_desc", 
   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min} -- {max}"), 
    Metric = case_when(
      metric == "size" ~ "Team size", 
      metric == "years_from_phd" ~ "Years since PhD", 
      metric == "stat_rating" ~ "Self-report statistical ability", 
      metric == "prior_belief" ~ "Prior belief in $H_{1}$", 
      metric == "phon_rating" ~ "Acoustic analysis rating", 
      metric == "all_rating" ~ "Overall peer review rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)

@@

# Model descriptives 
tbl_model_desc <- msa_models %>% 
  select(animal, n_predictors:n_random, n_models) %>% 
  group_by(animal) %>% 
  summarize(across(everything(), mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
  mutate(desc = "model_desc", 
    metric = fct_relevel(metric, "n_models"), 
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min} -- {max}"), 
    Metric = case_when(
      metric == "n_coefficients" ~ "n. coefficients", 
      metric == "n_models" ~ "n. models", 
      metric == "n_predictors" ~ "n. predictors", 
      metric == "n_random" ~ "n. random effects", 
      metric == "n_random_int" ~ "n. random intercepts", 
      metric == "n_random_slo" ~ "n. random slopes", 
      metric == "n_random_smooth" ~ "n. random smooths",
      metric == "n_terms" ~ "n. terms"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

@@

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", sd)`) models per team. 
Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

<!-- Begin Table 1 --> 
\vspace{0.2in}
```{r}
#| label: team-descriptives-table
#| results: 'asis'
#| eval: false
  tbl_team_desc %>% 
  select(Metric, Range, `Mean (SD)`) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "r", "r"), 
    caption = "Descriptive statistics for teams included in the 
    meta-analysis (n = 30).",
    label = "team-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)
```
<!-- END: Table -->

@@

`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models used acoustic measures taken at the level of the segment (e.g. comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g. comparing the acoustic profile of *Banane* 'banana'), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g. the noun phrase including determiner and adjective, e.g. "the green banana"), `r round(window_n[[4,1]],2) * 100`\% from the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence. 
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
Table \@ref(tab:descriptives-table) provides a summary of the acoustic analyses.

<!-- Begin Table 2 --> 
\vspace{0.2in}
```{r}
#| label: categorical-descriptives-table
#| results: 'asis'
#| eval: false

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
An appropriate way to account for this non-independence is by using models that include so-called random or group level effects [e.g., @gelman2006data; @schielzeth2009conclusions], variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication]. <!-- TR: Did we confirm this? -->
`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
Table \@ref(tab:descriptives-table) provides a summary of the statistical analyses.

<!-- Found effect 
JVC: this code is ready to go, but not all the rows in the google sheet are 
filled out (approx. 40 missing)
--> 
```{r}
#| label: found-effect

@@

<!-- Begin Table 3 --> 
```{r}
#| label: stats-descriptives-table
#| results: 'asis'
#| eval: false
tbl_model_desc %>% 
  select(Metric, Range, `Mean (SD)`) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. "), 
         Metric = str_to_sentence(Metric)) %>% 
  knitr::kable(format = "latex", booktabs = T, escape = F, 
    linesep = "", align = c("l", "l", "r"), 
    caption = "Descriptive statistics for statistical analyses included in the 
    meta-analysis (n = 30).",
    label = "stats-descriptives-table"
    ) %>% 
  kableExtra::kable_styling(., font_size = 11)
```
<!-- END: Table -->

```{r}
#| label: descriptives-table
#| results: 'asis'
library(kableExtra)
bind_rows(
  tbl_team_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
  tbl_categorical_desc %>% 
    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
    mutate(val1 = glue::glue("{val1}")), 
  tbl_model_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
) %>% 
  mutate(order = c(
    1, 6, 5, 4, 3, 2, 
    21, 20, 23, 22, 24, 
    8, 7, 10, 9, 11, 
    16, 15, 12, 14, 13, 
    17, 18, 19, 
    26, 25, 27, 28, 29, 30, 31, 32
    )
  ) %>% 
  arrange(order) %>% 
  select(-order) %>% 
  mutate(desc = str_replace_all(desc, "team_desc", " "), 
    desc = str_replace_all(desc, "model_desc", "N"), 
    desc = case_when(
      Metric != "n. models" & desc == "N" ~ " ", 
      Metric != "Frequentist" & desc == "Framework" ~ " ", 
      Metric != "Linear model" & desc == "Model" ~ " ", 
      Metric != "F0" & desc == "Outcome" ~ " ", 
      Metric != "Segment" & desc == "Temporal window" ~ " ", 
      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
      TRUE ~ desc)
    ) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. "), 
         Metric = str_to_sentence(Metric)) %>% 
  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
    `\\bf{Mean (SD)}` = val2) %>% 
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ",  .before = 14) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 20) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 24) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 25) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 32) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
    .before = 33) %>%
  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
    longtable = F, linesep = "", 
    caption = "Descriptive statistics of contributing teams (n = 30), acoustic 
    analyses, and statistical analyses.",
    label = "descriptives-table") %>% 
  kable_styling(full_width = F, latex_options = "scale_down") %>% 
  add_indent(c(9, 15, 21, 26, 29, 34)) %>% 
  row_spec(8, hline_after = T) %>% 
  row_spec(25, hline_after = T)
```

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:descriptives-table)).
The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).
For reference, as mentioned in the Methods section, a score of 75 was defined as "an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation", indicating that on average reviewers judged the provided analyses to be appropriate, although "imperfect".

### 2022-09-23 RR_manuscript/Draft_RR.tex
add one giant table for feedback

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.7 (SD: 3.4) models per team.
Table \ref{tab:team-descriptives-table} provides a summary of the contributing teams and their analyses.
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

\vspace{0.2in}
\begin{table}

\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams included in the 
    meta-analysis (n = 30).}
\centering
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{lcr}
\toprule
Metric & Range & Mean (SD)\\
\midrule
Team size & 1.0--12.0 & 3.6 (2.8)\\
Overall peer review rating & 39.0--88.7 & 70.0 (14.3)\\
Acoustic analysis rating & 41.2--88.3 & 71.5 (13.9)\\
Prior belief in $H_{1}$ & 48.5--92.0 & 69.2 (11.3)\\
Self-report statistical ability & 33.0--93.3 & 69.5 (16.5)\\
Years since PhD & -3.8--12.4 & 4.8 (4.2)\\
n. models & 1--16 & 3.7 (3.4)\\
\bottomrule
\end{tabular}
\end{table}

@@

Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
Table \ref{tab:categorical-descriptives-table} provides a summary of the acoustic analyses.

\vspace{0.2in}
\begin{table}

\caption{\label{tab:categorical-descriptives-table}Descriptive statistics for model stuff.}
\centering
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{llrr}
\toprule
Metric & Type & n & \%\\
\midrule
Framework & Frequentist & 86 & 82.7\\
 & Bayesian & 18 & 17.3\\
 &  &  & \\
Model & Linear model & 102 & 98.1\\
 & GAM & 1 & 1.0\\
 & Other & 1 & 1.0\\
 &  &  & \\
Outcome & F0 & 37 & 35.6\\
 & Duration & 36 & 34.6\\
 & Intensity & 15 & 14.4\\
 & Formants & 13 & 12.5\\
 & Other & 3 & 2.9\\
 &  &  & \\
Temporal window & Segment & 47 & 45.6\\
 & Word & 45 & 43.7\\
 & Other & 4 & 3.9\\
 & Sentence & 4 & 3.9\\
 & Phrase & 3 & 2.9\\
 &  &  & \\
Typicality operationalization & Categorical & 75 & 72.8\\
 & Continuous (mean) & 25 & 24.3\\
 & Continuous (median) & 3 & 2.9\\
\bottomrule
\end{tabular}
\end{table}

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
8\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
65\% specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included 2.5 random terms in their models.
Table \ref{tab:stats-descriptives-table} provides a summary of the statistical analyses.

@@

\caption{\label{tab:stats-descriptives-table}Descriptive statistics for statistical analyses included in the 
    meta-analysis (n = 30).}
\centering
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{lcr}
\toprule
Metric & Range & Mean (SD)\\
\midrule
Coefficients & 1--11 & 3.5 (2.7)\\
Models & 1--16 & 3.7 (3.4)\\
Predictors & 1--4 & 1.6 (0.9)\\
Random effects & 0--10 & 2.5 (2.1)\\
Random intercepts & 0--10 & 1.9 (1.8)\\
Random slopes & 0--4 & 0.6 (1.1)\\
Terms & 1--4 & 1.8 (1.1)\\
\bottomrule
\end{tabular}
\end{table}

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:team-descriptives-table}).
The mean rating of the statistical analysis is 73.8 (SD = 14.1).
For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.

>>>>

At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.7 (SD: 3.4) models per team.
Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.

\vspace{0.2in}

@@

Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
Table \ref{tab:descriptives-table} provides a summary of the acoustic analyses.

\vspace{0.2in}

@@

The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
8\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
65\% specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included 2.5 random terms in their models.
Table \ref{tab:descriptives-table} provides a summary of the statistical analyses.

@@

\caption{\label{tab:descriptives-table}Descriptive statistics of contributing teams (n = 30), acoustic 
    analyses, and statistical analyses.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
\bf{Team characteristics} &    & \bf{Range} & \bf{Mean (SD)}\\
\midrule
 & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
 & Years since phd & -3.8 -- 12.4 & 4.8 (4.2)\\
 & Self-report statistical ability & 33.0 -- 93.3 & 69.5 (16.5)\\
 & Prior belief in $h_{1}$ & 48.5 -- 92.0 & 69.2 (11.3)\\
 & Acoustic analysis rating & 41.2 -- 88.3 & 71.5 (13.9)\\
 & Overall peer review rating & 39.0 -- 88.7 & 70.0 (14.3)\\
 &  &  \vphantom{5} & \\
\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Outcome & F0 & 37 & 35.6\\
 & Duration & 36 & 34.6\\
 & Intensity & 15 & 14.4\\
 & Formants & 13 & 12.5\\
 & Other & 3 & 2.9\\
 &  &  \vphantom{4} & \\
\hspace{1em}Temporal window & Segment & 47 & 45.6\\
 & Word & 45 & 43.7\\
 & Sentence & 4 & 3.9\\
 & Phrase & 3 & 2.9\\
 & Other & 4 & 3.9\\
 &  &  \vphantom{3} & \\
\hspace{1em}Typicality operationalization & Categorical & 75 & 72.8\\
 & Continuous (mean) & 25 & 24.3\\
 & Continuous (median) & 3 & 2.9\\
 &  &  \vphantom{2} & \\
\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
\midrule
\hspace{1em}Framework & Frequentist & 86 & 82.7\\
 & Bayesian & 18 & 17.3\\
 &  &  \vphantom{1} & \\
\hspace{1em}Model & Linear model & 102 & 98.1\\
 & Gam & 1 & 1.0\\
 & Other & 1 & 1.0\\
 &  &  & \\
 &  & \bf{Range} & \bf{Mean (SD)}\\
\hspace{1em}N & Models & 1 -- 16 & 3.7 (3.4)\\
 & Coefficients & 1 -- 11 & 3.5 (2.7)\\
 & Predictors & 1 -- 4 & 1.6 (0.9)\\
 & Random effects & 0 -- 10 & 2.5 (2.1)\\
 & Random intercepts & 0 -- 10 & 1.9 (1.8)\\
 & Random slopes & 0 -- 4 & 0.6 (1.1)\\
 & Terms & 1 -- 4 & 1.8 (1.1)\\
\bottomrule
\end{tabular}}
\end{table}

@@

Teams reviewed each others' acoustic and statistical analyses.
The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:descriptives-table}).
The mean rating of the statistical analysis is 73.8 (SD = 14.1).
For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
